Computer Science House Constitution

### 2020-04-12 constitution.tex
Correct inconsistency in Intro Period extensions
Correct undefined Resignation references
Resignation -> Executive Board Resignation

		The vacated office is then handled like any other vacated office; see \ref{Resignations}.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting.
		The member(s) initiating the petition present their case to the Executive Board.
		The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
		If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed.
		This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
		Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official.
		A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
		If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.
\end{enumerate}

>>>>

		The vacated office is then handled like any other vacated office; see \ref{Executive Board Resignations}.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting.
		The member(s) initiating the petition present their case to the Executive Board.
		The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
		If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed.
		This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
		Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official.
		A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office.
		If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
		A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Executive Board Resignations}.
	\item House Secretary can be impeached according to the above process, or may be dismissed by a Simple Majority vote of the Executive Board.
\end{enumerate}
